---
title: "TADPOLE_BSWiMS"
author: "Jose Tamez"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    fig_caption: yes
    number_sections: yes
  word_document: 
    reference_docx: WordStyle_FRESA.docx
    toc: yes
    fig_caption: yes
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(collapse = TRUE, warning = FALSE, message = FALSE,comment = "#>")
```

# TADPOLE and BSWiMS

### Loading the libraries

```{r}
library("FRESA.CAD")
library(survival)
library(readxl)
library(igraph)
op <- par(no.readonly = TRUE)
pander::panderOptions('digits', 3)
pander::panderOptions('table.split.table', 400)
pander::panderOptions('keep.trailing.zeros',TRUE)

```

## The data set

```{r}
setwd("~")
TADPOLE_D1_D2 <- read.csv("~/GitHub/SurvivalTadpole/Data/TADPOLE/TADPOLE_D1_D2.csv")
TADPOLE_D1_D2_Dict <- read.csv("~/GitHub/SurvivalTadpole/Data/TADPOLE/TADPOLE_D1_D2_Dict.csv")
TADPOLE_D1_D2_Dict_LR <- as.data.frame(read_excel("~/GitHub/SurvivalTadpole/Data/TADPOLE/TADPOLE_D1_D2_Dict_LR.xlsx",sheet = "LeftRightFeatures"))


rownames(TADPOLE_D1_D2_Dict) <- TADPOLE_D1_D2_Dict$FLDNAME

```

## Conditioning the data

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}

# mm3 to mm
isVolume <- c("Ventricles","Hippocampus","WholeBrain","Entorhinal","Fusiform","MidTemp","ICV",
              TADPOLE_D1_D2_Dict$FLDNAME[str_detect(TADPOLE_D1_D2_Dict$TEXT,"Volume")]
              )


#TADPOLE_D1_D2[,isVolume] <- apply(TADPOLE_D1_D2[,isVolume],2,'^',(1/3))
TADPOLE_D1_D2[,isVolume] <- TADPOLE_D1_D2[,isVolume]^(1/3)

# mm2 to mm
isArea <- TADPOLE_D1_D2_Dict$FLDNAME[str_detect(TADPOLE_D1_D2_Dict$TEXT,"Area")]
TADPOLE_D1_D2[,isArea] <- sqrt(TADPOLE_D1_D2[,isArea])

# Get only cross sectional measurements
FreeSurfersetCross <- str_detect(colnames(TADPOLE_D1_D2),"UCSFFSX")

# The subset of baseline measurements
baselineTadpole <- subset(TADPOLE_D1_D2,VISCODE=="bl")
table(baselineTadpole$DX)

rownames(baselineTadpole) <- baselineTadpole$PTID


validBaselineTadpole <- cbind(DX=baselineTadpole$DX,
                                 AGE=baselineTadpole$AGE,
                                 Gender=1*(baselineTadpole$PTGENDER=="Female"),
                                 ADAS11=baselineTadpole$ADAS11,
                                 ADAS13=baselineTadpole$ADAS13,
                                 MMSE=baselineTadpole$MMSE,
                                 RAVLT_immediate=baselineTadpole$RAVLT_immediate,
                                 RAVLT_learning=baselineTadpole$RAVLT_learning,
                                 RAVLT_forgetting=baselineTadpole$RAVLT_forgetting,
                                 RAVLT_perc_forgetting=baselineTadpole$RAVLT_perc_forgetting,
                                 FAQ=baselineTadpole$FAQ,
                                 APOE4=1*(as.numeric(baselineTadpole$APOE4)>0),
                                 Ventricles=baselineTadpole$Ventricles,
                                 Hippocampus=baselineTadpole$Hippocampus,
                                 WholeBrain=baselineTadpole$WholeBrain,
                                 Entorhinal=baselineTadpole$Entorhinal,
                                 Fusiform=baselineTadpole$Fusiform,
                                 MidTemp=baselineTadpole$MidTemp,
                                 ICV=baselineTadpole$ICV,
                                 ABETA=as.numeric(baselineTadpole$ABETA_UPENNBIOMK9_04_19_17),
                                 TAU=as.numeric(baselineTadpole$TAU_UPENNBIOMK9_04_19_17),
                                 PTAU=as.numeric(baselineTadpole$PTAU_UPENNBIOMK9_04_19_17),
                                 baselineTadpole[,FreeSurfersetCross])

pander::pander(summary(validBaselineTadpole$APOE4))
pander::pander(summary(validBaselineTadpole$ABETA))
pander::pander(summary(validBaselineTadpole$TAU))
pander::pander(summary(validBaselineTadpole$PTAU))

fraction <- sum(is.na(validBaselineTadpole$PTAU)/nrow(validBaselineTadpole))
pander::pander(c(col=ncol(validBaselineTadpole),row=nrow(validBaselineTadpole)))


LeftFields <- TADPOLE_D1_D2_Dict_LR$LFN
names(LeftFields) <- LeftFields
LeftFields <- LeftFields[LeftFields %in% colnames(validBaselineTadpole)]
RightFields <- TADPOLE_D1_D2_Dict_LR$RFN
names(RightFields) <- RightFields
RightFields <- RightFields[RightFields %in% colnames(validBaselineTadpole)]

## Normalize to ICV
validBaselineTadpole$Ventricles=validBaselineTadpole$Ventricles/validBaselineTadpole$ICV
validBaselineTadpole$Hippocampus=validBaselineTadpole$Hippocampus/validBaselineTadpole$ICV
validBaselineTadpole$WholeBrain=validBaselineTadpole$WholeBrain/validBaselineTadpole$ICV
validBaselineTadpole$Entorhinal=validBaselineTadpole$Entorhinal/validBaselineTadpole$ICV
validBaselineTadpole$Fusiform=validBaselineTadpole$Fusiform/validBaselineTadpole$ICV
validBaselineTadpole$MidTemp=validBaselineTadpole$MidTemp/validBaselineTadpole$ICV

leftData <- validBaselineTadpole[,LeftFields]/validBaselineTadpole$ICV
RightData <- validBaselineTadpole[,RightFields]/validBaselineTadpole$ICV

## get mean and relative difference 
meanLeftRight <- (leftData + RightData)/2
difLeftRight <- abs(leftData - RightData)
reldifLeftRight <- difLeftRight/meanLeftRight
colnames(meanLeftRight) <- paste("M",colnames(meanLeftRight),sep="_")
colnames(difLeftRight) <- paste("D",colnames(difLeftRight),sep="_")
colnames(reldifLeftRight) <- paste("RD",colnames(reldifLeftRight),sep="_")


validBaselineTadpole <- validBaselineTadpole[,!(colnames(validBaselineTadpole) %in% 
                                               c(LeftFields,RightFields))]
validBaselineTadpole <- cbind(validBaselineTadpole,meanLeftRight,reldifLeftRight)

## Remove columns with too many NA more than %35 of NA
nacount <- apply(is.na(validBaselineTadpole),2,sum)/nrow(validBaselineTadpole) <= fraction
diagnose <- validBaselineTadpole$DX
pander::pander(table(diagnose))
validBaselineTadpole <- validBaselineTadpole[,nacount]
## Remove character columns
ischar <- sapply(validBaselineTadpole,class) == "character"
validBaselineTadpole <- validBaselineTadpole[,!ischar]
## Place back diagnose
validBaselineTadpole$DX <- diagnose

pander::pander(summary(validBaselineTadpole$APOE4))
pander::pander(summary(validBaselineTadpole$ABETA))
pander::pander(summary(validBaselineTadpole$TAU))
pander::pander(summary(validBaselineTadpole$PTAU))

pander::pander(c(col=ncol(validBaselineTadpole),row=nrow(validBaselineTadpole)))




validBaselineTadpole <- validBaselineTadpole[complete.cases(validBaselineTadpole),]
ischar <- sapply(validBaselineTadpole,class) == "character"
validBaselineTadpole[,!ischar] <- sapply(validBaselineTadpole[,!ischar],as.numeric)

pander::pander(summary(validBaselineTadpole$APOE4))
pander::pander(summary(validBaselineTadpole$ABETA))
pander::pander(summary(validBaselineTadpole$TAU))
pander::pander(summary(validBaselineTadpole$PTAU))

pander::pander(c(col=ncol(validBaselineTadpole),row=nrow(validBaselineTadpole)))

colnames(validBaselineTadpole) <- str_remove_all(colnames(validBaselineTadpole),"_UCSFFSX_11_02_15_UCSFFSX51_08_01_16")
colnames(validBaselineTadpole) <- str_replace_all(colnames(validBaselineTadpole)," ","_")
validBaselineTadpole$LONISID <- NULL
validBaselineTadpole$IMAGEUID <- NULL
validBaselineTadpole$LONIUID <- NULL

diagnose <- as.character(validBaselineTadpole$DX)
validBaselineTadpole$DX <- diagnose
pander::pander(table(validBaselineTadpole$DX))


validDX <- c("NL","MCI","Dementia")

validBaselineTadpole <- validBaselineTadpole[validBaselineTadpole$DX %in% validDX,]
validBaselineTadpole$DX <- as.factor(validBaselineTadpole$DX)
pander::pander(table(validBaselineTadpole$DX))



```

### Correlation Matrix  Data

The heat map of the testing set.

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}

cormat <- cor(validBaselineTadpole[,colnames(validBaselineTadpole) != "DX"],method="spearman")
diag(cormat) <- 0;
corrmax <- apply(cormat,2,max)
whomax <- colnames(cormat)[corrmax>0.75]
gplots::heatmap.2(abs(cormat[whomax,whomax]),
                  trace = "none",
                  scale = "none",
                  mar = c(10,10),
                  col=rev(heat.colors(5)),
                  main = "Baseline TADPOLE Correlation",
                  cexRow = 0.5,
                  cexCol = 0.5,
                  key.title=NA,
                  key.xlab="Spearman Correlation",
                  xlab="Feature", ylab="Feature")
par(op)

```


## Get the Time To Event on MCI Subjects

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}

subjectsID <- rownames(validBaselineTadpole)
visitsID <- unique(TADPOLE_D1_D2$VISCODE)
baseDx <- TADPOLE_D1_D2[TADPOLE_D1_D2$VISCODE=="bl",c("PTID","DX","EXAMDATE")]
rownames(baseDx) <- baseDx$PTID 
baseDx <- baseDx[subjectsID,]
lastDx <- baseDx
toDementia <- baseDx
table(lastDx$DX)
hasDementia <- lastDx$PTID[str_detect(lastDx$DX,"Dementia")]


for (vid in visitsID)
{
  DxValue <- TADPOLE_D1_D2[TADPOLE_D1_D2$VISCODE==vid,c("PTID","DX","EXAMDATE")]
  rownames(DxValue) <- DxValue$PTID 
  DxValue <- DxValue[DxValue$PTID %in% subjectsID,]
  noDX <- DxValue$PTID[nchar(DxValue$DX) < 1]
  print(length(noDX))
  DxValue[noDX,] <- lastDx[noDX,]
  inLast <- lastDx$PTID[lastDx$PTID %in% DxValue$PTID]
  print(length(inLast))
  lastDx[inLast,] <- DxValue[inLast,]
  noDementia <- !(toDementia$PTID %in% hasDementia)
  toDementia[noDementia,] <- lastDx[noDementia,]
  hasDementia <- unique(c(hasDementia,lastDx$PTID[str_detect(lastDx$DX,"Dementia")]))
}
table(lastDx$DX)
baseMCI <-baseDx$PTID[baseDx$DX == "MCI"]
lastDementia <- lastDx$PTID[str_detect(lastDx$DX,"Dementia")]
lastDementia2 <- toDementia$PTID[str_detect(toDementia$DX,"Dementia")]
lastNL <- lastDx$PTID[str_detect(lastDx$DX,"NL")]

MCIatBaseline <- baseDx[baseMCI,]
MCIatEvent <- toDementia[baseMCI,]
MCIatLast <- lastDx[baseMCI,]

MCIconverters <- MCIatBaseline[baseMCI %in% lastDementia,]
MCI_No_converters <- MCIatBaseline[!(baseMCI %in% MCIconverters$PTID),]
MCIconverters$TimeToEvent <- (as.Date(toDementia[MCIconverters$PTID,"EXAMDATE"]) 
                                   - as.Date(MCIconverters$EXAMDATE))

sum(MCIconverters$TimeToEvent ==0)


MCIconverters$AtEventDX <- MCIatEvent[MCIconverters$PTID,"DX"]
MCIconverters$LastDX <- MCIatLast[MCIconverters$PTID,"DX"]

MCI_No_converters$TimeToEvent <- (as.Date(lastDx[MCI_No_converters$PTID,"EXAMDATE"]) 
                                   - as.Date(MCI_No_converters$EXAMDATE))

MCI_No_converters$LastDX <- MCIatLast[MCI_No_converters$PTID,"DX"]

MCI_No_converters <- subset(MCI_No_converters,TimeToEvent > 0)



```

# Prognosis MCI to AD Conversion

## the set
```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}
TrainFraction <- 0.70;

MCIPrognosisIDs <- c(MCIconverters$PTID,MCI_No_converters$PTID)

TADPOLECrossMRI <- validBaselineTadpole[MCIPrognosisIDs,]


table(TADPOLECrossMRI$DX)
TADPOLECrossMRI$DX <- NULL
TADPOLECrossMRI$status <- 1*(rownames(TADPOLECrossMRI) %in% MCIconverters$PTID)
table(TADPOLECrossMRI$status)
TADPOLECrossMRI$TimeToEvent <- numeric(nrow(TADPOLECrossMRI))
TADPOLECrossMRI[MCIconverters$PTID,"TimeToEvent"] <- MCIconverters$TimeToEvent
TADPOLECrossMRI[MCI_No_converters$PTID,"TimeToEvent"] <- MCI_No_converters$TimeToEvent
TADPOLECrossMRI$TimeToEvent <- TADPOLECrossMRI$TimeToEvent/365.25


TADPOLE_Cases <- subset(TADPOLECrossMRI,status==1)
TADPOLE_Controls <- subset(TADPOLECrossMRI,status==0)
trainCasesSet <- sample(nrow(TADPOLE_Cases),nrow(TADPOLE_Cases)*TrainFraction)
trainControlSet <- sample(nrow(TADPOLE_Controls),nrow(TADPOLE_Controls)*TrainFraction)

TADPOLE_Conv_TRAIN <- rbind(TADPOLE_Cases[trainCasesSet,],TADPOLE_Controls[trainControlSet,])
TADPOLE_Conv_TEST <- TADPOLECrossMRI[!(rownames(TADPOLECrossMRI) %in%
                                         rownames(TADPOLE_Conv_TRAIN)),]

pander::pander(table(TADPOLE_Conv_TRAIN$status))
pander::pander(table(TADPOLE_Conv_TEST$status))

pander::pander(c(col=ncol(TADPOLECrossMRI),row=nrow(TADPOLECrossMRI)))

par(op)



```

### Number of subjects
```{r results = "asis"}

pander::pander(c(col=ncol(baselineTadpole),row=nrow(baselineTadpole)))
pander::pander(c(col=ncol(validBaselineTadpole),row=nrow(validBaselineTadpole)))
pander::pander(c(col=ncol(TADPOLECrossMRI),row=nrow(TADPOLECrossMRI)))

```

### Data Summary

```{r results = "asis", warning = FALSE}
varlist <- colnames(TADPOLECrossMRI);
varlist <- varlist[varlist != "status"]
varlist <- varlist[1:21]
varlist <- cbind(varlist,varlist)
uvar <- uniRankVar(variableList=varlist,
                   formula="Surv(TimeToEvent,status)~1",
                   Outcome="status",
                   data=TADPOLECrossMRI,
                   timeOutcome="TimeToEvent")

colnames(uvar$orderframe)
uninames <- c("caseMean","caseStd","controlMean","controlStd","Beta","ZGLM")   


pander::pander(uvar$orderframe[,uninames])
```


### Cross Validation all Features

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}



cvBSWiMSRaw <- randomCV(TADPOLECrossMRI,
                 Surv(TimeToEvent,status)~.,
                 fittingFunction= BSWiMS.model,
                 classSamplingType = "Ba",
                 trainFraction = 0.75,
                 repetitions = 50,
                 loops=1,
 )

pander::pander(cbind(cvBSWiMSRaw$featureFrequency[cvBSWiMSRaw$featureFrequency>20]))

par(op)
survmtest <- cvBSWiMSRaw$survMedianTest
survmtest <- survmtest[complete.cases(survmtest),]

prBin <- predictionStats_binary(cvBSWiMSRaw$survMedianTrain[,c(2,3)],"Train: MCI to  AD Conversion")
prBin <- predictionStats_binary(survmtest[,c(2,3)],"BSWiMS: MCI to  AD Conversion")
allBinROC <- prBin


pander::pander(prBin$aucs)
pander::pander(prBin$CM.analysis$tab)

par(op)
ho <- mean(survmtest$Outcome)
timeInterval <- mean(survmtest[survmtest$Outcome==0,"Times"])
pgzero <- ppoisGzero(survmtest$LinearPredictorsMedian,ho)
rsdata <- cbind(survmtest$Outcome,pgzero,survmtest$Times)
riskAnalysis <- RRPlot(rsdata,riskTimeInterval=timeInterval,title="BSWiMS")


pander::pander(riskAnalysis$keyPoints)

pander::pander(riskAnalysis$c.index)
pander::pander(riskAnalysis$ROCAnalysis$aucs)
pander::pander(riskAnalysis$cenAUC)
pander::pander(riskAnalysis$ROCAnalysis$ClassMetrics)
pander::pander(riskAnalysis$surdif)


```


### Cross Validation Cog Features

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}

survCol <- c("TimeToEvent","status")
OnlyCogTest <- c("ADAS11",
                 "ADAS13",
                 "MMSE",
                 "RAVLT_immediate",
                 "RAVLT_learning",
                 "RAVLT_forgetting",
                 "RAVLT_perc_forgetting",
                 "FAQ")

cvBSWiMSGog <- randomCV(TADPOLECrossMRI[,c(survCol,OnlyCogTest)],
                 Surv(TimeToEvent,status)~.,
                 fittingFunction= BSWiMS.model,
                trainSampleSets= cvBSWiMSRaw$trainSamplesSets,
                loops=1,
 )

pander::pander(cbind(cvBSWiMSGog$featureFrequency[cvBSWiMSGog$featureFrequency>20]))

par(op)
survmtest <- cvBSWiMSGog$survMedianTest
survmtest <- survmtest[complete.cases(survmtest),]

prBin <- predictionStats_binary(cvBSWiMSGog$survMedianTrain[,c(2,3)],"Train: MCI to  AD Conversion")
prBin <- predictionStats_binary(survmtest[,c(2,3)],"Cognitive: MCI to  AD Conversion")
allBinCog <- prBin

pander::pander(prBin$aucs)
pander::pander(prBin$CM.analysis$tab)

par(op)
ho <- mean(survmtest$Outcome)
timeInterval <- mean(survmtest[survmtest$Outcome==0,"Times"])
pgzero <- ppoisGzero(survmtest$LinearPredictorsMedian,ho)
rsdata <- cbind(survmtest$Outcome,pgzero,survmtest$Times)
riskAnalysis <- RRPlot(rsdata,riskTimeInterval=timeInterval,title="Cognitive")


pander::pander(riskAnalysis$keyPoints)

pander::pander(riskAnalysis$c.index)
pander::pander(riskAnalysis$ROCAnalysis$aucs)
pander::pander(riskAnalysis$cenAUC)
pander::pander(riskAnalysis$ROCAnalysis$ClassMetrics)
pander::pander(riskAnalysis$surdif)


```

### Cross Validation Fluid Features

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}

OnlyFluid <- c("ABETA","TAU","PTAU","APOE4")

cvBSWiMSFluid <- randomCV(TADPOLECrossMRI[,c(survCol,OnlyFluid)],
                 Surv(TimeToEvent,status)~.,
                 fittingFunction= BSWiMS.model,
                trainSampleSets= cvBSWiMSRaw$trainSamplesSets,
                loops=1,
 )

pander::pander(cbind(cvBSWiMSFluid$featureFrequency[cvBSWiMSFluid$featureFrequency>20]))

par(op)
survmtest <- cvBSWiMSFluid$survMedianTest
survmtest <- survmtest[complete.cases(survmtest),]

prBin <- predictionStats_binary(cvBSWiMSFluid$survMedianTrain[,c(2,3)],"Train: MCI to  AD Conversion")
prBin <- predictionStats_binary(survmtest[,c(2,3)],"Fluid + Apoe: MCI to  AD Conversion")
allBinFluid <- prBin
pander::pander(prBin$aucs)
pander::pander(prBin$CM.analysis$tab)

par(op)
ho <- mean(survmtest$Outcome)
timeInterval <- mean(survmtest[survmtest$Outcome==0,"Times"])
pgzero <- ppoisGzero(survmtest$LinearPredictorsMedian,ho)
rsdata <- cbind(survmtest$Outcome,pgzero,survmtest$Times)
riskAnalysis <- RRPlot(rsdata,riskTimeInterval=timeInterval,title="Fluid + Apoe")


pander::pander(riskAnalysis$keyPoints)

pander::pander(riskAnalysis$c.index)
pander::pander(riskAnalysis$ROCAnalysis$aucs)
pander::pander(riskAnalysis$cenAUC)
pander::pander(riskAnalysis$ROCAnalysis$ClassMetrics)
pander::pander(riskAnalysis$surdif)


```


### Cross Validation MRI Features

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}

allNames <- colnames(TADPOLECrossMRI)
MRInames <- allNames[!(allNames %in% OnlyFluid | allNames %in% OnlyCogTest)]

cvBSWiMSMRI <- randomCV(TADPOLECrossMRI[,MRInames],
                 Surv(TimeToEvent,status)~.,
                 fittingFunction= BSWiMS.model,
                trainSampleSets= cvBSWiMSRaw$trainSamplesSets,
                loops=1,
 )

pander::pander(cbind(cvBSWiMSMRI$featureFrequency[cvBSWiMSMRI$featureFrequency>20]))

par(op)
survmtest <- cvBSWiMSMRI$survMedianTest
survmtest <- survmtest[complete.cases(survmtest),]

prBin <- predictionStats_binary(cvBSWiMSMRI$survMedianTrain[,c(2,3)],"Train: MCI to  AD Conversion")
prBin <- predictionStats_binary(survmtest[,c(2,3)],"MRI: MCI to  AD Conversion")
allBinMRI <- prBin

pander::pander(prBin$aucs)
pander::pander(prBin$CM.analysis$tab)

par(op)
ho <- mean(survmtest$Outcome)
timeInterval <- mean(survmtest[survmtest$Outcome==0,"Times"])
pgzero <- ppoisGzero(survmtest$LinearPredictorsMedian,ho)
rsdata <- cbind(survmtest$Outcome,pgzero,survmtest$Times)
riskAnalysis <- RRPlot(rsdata,riskTimeInterval=timeInterval,title="MRI")


pander::pander(riskAnalysis$keyPoints)

pander::pander(riskAnalysis$c.index)
pander::pander(riskAnalysis$ROCAnalysis$aucs)
pander::pander(riskAnalysis$cenAUC)
pander::pander(riskAnalysis$ROCAnalysis$ClassMetrics)
pander::pander(riskAnalysis$surdif)


```


### Cross Validation MRI and Cog Features

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}

cvBSWiMSMRICog <- randomCV(TADPOLECrossMRI[,c(MRInames,OnlyCogTest)],
                 Surv(TimeToEvent,status)~.,
                 fittingFunction= BSWiMS.model,
                trainSampleSets= cvBSWiMSRaw$trainSamplesSets,
                loops=1,
 )

pander::pander(cbind(cvBSWiMSMRICog$featureFrequency[cvBSWiMSMRICog$featureFrequency>20]))

par(op)
survmtest <- cvBSWiMSMRICog$survMedianTest
survmtest <- survmtest[complete.cases(survmtest),]

prBin <- predictionStats_binary(cvBSWiMSMRICog$survMedianTrain[,c(2,3)],"Train: MCI to  AD Conversion")
prBin <- predictionStats_binary(survmtest[,c(2,3)],"MRI + Cog: MCI to  AD Conversion")
allBinMRICog <- prBin
pander::pander(prBin$aucs)
pander::pander(prBin$CM.analysis$tab)

par(op)
ho <- mean(survmtest$Outcome)
timeInterval <- mean(survmtest[survmtest$Outcome==0,"Times"])
pgzero <- ppoisGzero(survmtest$LinearPredictorsMedian,ho)
rsdata <- cbind(survmtest$Outcome,pgzero,survmtest$Times)
riskAnalysis <- RRPlot(rsdata,riskTimeInterval=timeInterval,title="MRI + Cog")


pander::pander(riskAnalysis$keyPoints)

pander::pander(riskAnalysis$c.index)
pander::pander(riskAnalysis$ROCAnalysis$aucs)
pander::pander(riskAnalysis$cenAUC)
pander::pander(riskAnalysis$ROCAnalysis$ClassMetrics)
pander::pander(riskAnalysis$surdif)


```

### Comparing ROC AUC

```{r}

ROCAUC <- rbind(All=allBinROC$aucs,
                Cog=allBinCog$aucs,
                CSF=allBinFluid$aucs,
                MRI=allBinMRI$aucs,
                COG_MRI=allBinMRICog$aucs)

ROCAUC <- ROCAUC[order(-ROCAUC[,1]),]
pander::pander(ROCAUC)

pander::pander(roc.test(allBinROC$ROC.analysis$roc.predictor,allBinMRICog$ROC.analysis$roc.predictor))
pander::pander(roc.test(allBinMRICog$ROC.analysis$roc.predictor,allBinCog$ROC.analysis$roc.predictor))
pander::pander(roc.test(allBinMRICog$ROC.analysis$roc.predictor,allBinMRI$ROC.analysis$roc.predictor))
pander::pander(roc.test(allBinMRICog$ROC.analysis$roc.predictor,allBinFluid$ROC.analysis$roc.predictor))
pander::pander(roc.test(allBinCog$ROC.analysis$roc.predictor,allBinMRI$ROC.analysis$roc.predictor))
pander::pander(roc.test(allBinMRI$ROC.analysis$roc.predictor,allBinFluid$ROC.analysis$roc.predictor))

```

### Learning

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}

bConvml <- BSWiMS.model(Surv(TimeToEvent,status)~1,TADPOLE_Conv_TRAIN,NumberofRepeats = 20)
pander::pander(bConvml$bagging$Jaccard.SM)

fs <- bConvml$bagging$frequencyTable
barplot(fs[order(-fs)],las=2,main="Selected Features",cex.names = 0.5)
sm <- summary(bConvml)
pander::pander(sm$coefficients)
pander::pander(bConvml$univariate[bConvml$selectedfeatures,])

ptestl <- predict(bConvml,TADPOLE_Conv_TEST,type="lp")
boxplot(ptestl~TADPOLE_Conv_TEST$status)
ptestr <- predict(bConvml,TADPOLE_Conv_TEST,type="risk")
eventCases <- subset(TADPOLE_Conv_TEST,status==1)
plot(1.0/ptestr[rownames(eventCases)]~eventCases$TimeToEvent)
pander::pander(cor.test(eventCases$TimeToEvent,1.0/ptestr[rownames(eventCases)],method="spearman"))



perdsurv <- as.data.frame(cbind(Times=TADPOLE_Conv_TEST$TimeToEvent,
                  Outcome=TADPOLE_Conv_TEST$status,
                  LinearPredictors=ptestl,
                  ptestr))
prSurv <- predictionStats_survival(perdsurv,"BSWiMS: MCI to  AD Conversion")
pander::pander(prSurv$CIRisk)
pander::pander(prSurv$CILp)
pander::pander(prSurv$spearmanCI)

prBin <- predictionStats_binary(cbind(TADPOLE_Conv_TEST$status,ptestl),"BSWiMS: MCI to  AD Conversion")
pander::pander(prBin$aucs)
pander::pander(prBin$CM.analysis$tab)





par(op)
ho <- mean(perdsurv$Outcome)
timeInterval <- mean(perdsurv[perdsurv$Outcome==0,"Times"])
pgzero <- ppoisGzero(perdsurv$LinearPredictors,ho)
rsdata <- cbind(perdsurv$Outcome,pgzero,perdsurv$Times)
riskAnalysis <- RRPlot(rsdata,riskTimeInterval=timeInterval,title="Test")


pander::pander(riskAnalysis$keyPoints)

pander::pander(riskAnalysis$c.index)
pander::pander(riskAnalysis$ROCAnalysis$aucs)
pander::pander(riskAnalysis$cenAUC)
pander::pander(riskAnalysis$ROCAnalysis$ClassMetrics)
pander::pander(riskAnalysis$surdif)


```




### The formula network

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}
cmax <- apply(bConvml$bagging$formulaNetwork,2,max)
cnames <- names(cmax[cmax>=0.125])
cmax <- cmax[cnames]

adma <- bConvml$bagging$formulaNetwork[cnames,cnames]

adma[adma<0.15] <- 0;
gr <- graph_from_adjacency_matrix(adma,mode = "undirected",diag = FALSE,weighted=TRUE)
gr$layout <- layout_with_fr

fc <- cluster_optimal(gr)
plot(fc, gr,
     edge.width=5*E(gr)$weight,
     vertex.size=20*cmax,
     vertex.label.cex=0.75,
     vertex.label.dist=0,
     main="MCI to Dementia Conversion")
par(op)

```



### MCI to Dementia table
```{r}

clusterFeatures <- fc$names

tableMCI_to_Dem <- sm$coefficients[clusterFeatures,
                                   c("Estimate",
                                     "lower",
                                     "HR",
                                     "upper",
                                     "full.AUC",
                                     "Delta.AUC",
                                     "z.IDI",
                                     "Frequency")]

nugget <- fc$membership
names(nugget) <- clusterFeatures

tableMCI_to_Dem$Cluster <- nugget[rownames(tableMCI_to_Dem)]

rnames <- clusterFeatures[str_detect(clusterFeatures,"ST")]
frnames <- rnames
rnames <- str_replace_all(rnames,"M_","")
rnames <- str_replace_all(rnames,"RD_","")
rnames <- str_replace_all(rnames,"Ba_","")
rnames <- str_replace_all(rnames,"De_","")
description <- character()

for (ddet in c(1:length(rnames)))
{
  description <- c(description,TADPOLE_D1_D2_Dict$TEXT[str_detect(TADPOLE_D1_D2_Dict$FLDNAME,rnames[ddet])][1])
}
names(description) <- frnames

tableMCI_to_Dem$Description <- description[rownames(tableMCI_to_Dem)]
pander::pander(tableMCI_to_Dem)


```

### Heat map

```{r results = "asis", warning = FALSE, dpi=600, fig.height= 6.0, fig.width= 8.0}

hm <- heatMaps(Outcome="status",data=TADPOLECrossMRI[,c("status",clusterFeatures)],title="Heat Map",Scale=TRUE,
					   theFiveColors=c("black","red","orange","yellow","white"),
#					   theFiveColors=c("darkred","red","yellow","blue","darkblue"),
					   hCluster="col",
					   cexRow=0.50,cexCol=0.65,srtCol=35,
					   ylab="Subjects",
					   xlab="Features"
					   )

```

### Saving the enviroment
```{r}
save.image("./TADPOLE_BSWIMS_Results.RData")


```

